---
#==========================================================================================================================
title: "Neuronal Differentiation Paracet scATACSeq p2Glinksd0Ctrls "
author: "Ankush Sharma"
date: "`r Sys.Date()`"
output: html_document
Description: This script analyzes the peak2genelinks analysis for D20 Ctrl sample for kmeans of 5 of the manuscript  as seen in manuscript figure of Samara et al. 

#==========================================================================================================================
---




```{rloading Projects}
#load Projects IF entire code had been run once and user need to load the projects for further additional analysis

#paracetP1<-loadArchRProject("Save-paracetP1/")
#paracetP2<-loadArchRProject("Save-paracetP2/")
#paracetP3<-loadArchRProject("Save-paracetP3/")
#paracetP4<-loadArchRProject("Save-paracetP4/")
#paracetP5<-loadArchRProject("Save-paracetP5/")
```




```{r 1_library and work, include=FALSE}
#library(renv)
#renv::init()
#renv::activate()
library(ArchR)
library(progress)
library(hdf5r)
library(HDF5Array)
library(TFBSTools)
library(hexbin)
library(Seurat)
library(dplyr)
library(GenomicRanges)
library(gprofiler2)
library(data.table)
set.seed(1)

#(!requireNamespace("BSgenome.Hsapiens.UCSC.hg38", quietly = TRUE)){
#BiocManager::install("BSgenome.Hsapiens.UCSC.hg38")}#
#```{r Directories and other settings}
# Directory settings

addArchRGenome("hg38")
library(BSgenome.Hsapiens.UCSC.hg38)
#genomeAnnotation <- createGenomeAnnotation(genome = BSgenome.Hsapiens.UCSC.hg38)
#genomeAnnotation
library(org.Hs.eg.db)
#####
#if (!requireNamespace("BiocManager", quietly = TRUE))
# install.packages("BiocManager")
#BiocManager::install("TxDb.Hsapiens.UCSC.hg38.knownGene")
library(TxDb.Hsapiens.UCSC.hg38.knownGene)
currentjob <- "ProjDiff"
# Memory settings
options(future.globals.maxSize = 4000 * 1024^3) #Set a higher maximum memory size
addArchRThreads(threads = 1)

geneAnnotation <- createGeneAnnotation(TxDb = TxDb.Hsapiens.UCSC.hg38.knownGene, OrgDb = org.Hs.eg.db)
geneAnnotation <- createGeneAnnotation(
  TSS = geneAnnotation$TSS, 
  exons = geneAnnotation$exons, 
  genes = geneAnnotation$genes)

Differentiation_P_1 <- loadArchRProject('Save-paracetP1//')
Differentiation_P_2 <- loadArchRProject('Save-paracetP2/')
Differentiation_P_3 <- loadArchRProject('Save-paracetP3/')
Differentiation_P_4 <- loadArchRProject('Save-paracetP4/')
paracetP5 <- loadArchRProject('Save-paracetP5')
```


```{r addpeak2genelinks, include=FALSE} 
paracetP5 <- addPeak2GeneLinks(
    ArchRProj = paracetP5,
    reducedDims = "IterativeLSI",
    useMatrix = "GeneIntegrationMatrix"
    )
p2g <- getPeak2GeneLinks(
    ArchRProj = paracetP5,
    corCutOff = 0.45,
    resolution = 1,
    returnLoops = FALSE
)
p2g
metadata(p2g)
metadata(p2g)$seATAC


# Making Loop object from peak2gene link object p2g when return loop = FALSE

p2g$geneName <- mcols(metadata(p2g)$geneSet)$name[p2g$idxRNA]
tssgenes<- as.data.frame(metadata(p2g)$geneSet)
colnames(tssgenes)[2] <- "StartTSS"
colnames(tssgenes)[3] <- "EndTSS"
p2g$peakName <- (metadata(p2g)$peakSet %>% {paste0(seqnames(.), "_", start(.), "_", end(.))})[p2g$idxATAC]
p2g_df=as.data.frame(p2g)
temp  <- strsplit(p2g$peakName, "_")
temp <- matrix(unlist(temp), ncol=3, byrow=TRUE)
temp <- as.data.frame(temp)
p2g_df$chr <- temp$V1
p2g_df$start <- temp$V2
p2g_df$end <- temp$V3
mergedp2g <- merge(p2g_df,tssgenes ,by.x="geneName", by.y= "name")
mergedp2g$peakCentre=as.numeric(mergedp2g$start)+250
mergedp2g$looplength=as.numeric(mergedp2g$StartTSS)-as.numeric(mergedp2g$peakCentre)
#write data for p2glinks for all data
write.table(mergedp2g,"_Paracetd7d20_peak2genelinks_corr_0.45_res-1_loopobject.txt")

#getpeak2genelinks 
p2g <- getPeak2GeneLinks(
    ArchRProj = paracetP5,
    corCutOff = 0.45,
    resolution = 1,
    returnLoops = FALSE
    
)



```

#plotPeak2genelinkheatmap
```{r dataformat, include=FALSE} 

#Extracting Kmeans for the datafor all data
peak2genelinkmat <- plotPeak2GeneHeatmap(ArchRProj = paracetP5, groupBy = "Clusters2",
seed = 1,
  palATAC = paletteContinuous("coolwarm"),
  palRNA = paletteContinuous("blueYellow"),
  corCutOff = 0.45,
  FDRCutOff = 1e-04,
returnMatrices = TRUE,
nPlot = 100000 # all data
)
p2g_all <- as.data.frame(peak2genelinkmat@listData[["Peak2GeneLinks"]])
p2g_atac <- as.data.frame(peak2genelinkmat@listData[["ATAC"]]@listData[["kmeansId"]])
p2g_all$kmeansATAC <- p2g_atac$`peak2genelinkmat@listData[["ATAC"]]@listData[["kmeansId"]]`
p2g_rna <- as.data.frame(peak2genelinkmat@listData[["RNA"]]@listData[["kmeansId"]])
p2g_all$kmeansRNA <- p2g_rna$`peak2genelinkmat@listData[["RNA"]]@listData[["kmeansId"]]`
p2g_all$peak <- str_replace(p2g_all$peak,":","_")
p2g_all$peak <- str_replace(p2g_all$peak,"-","_")
p2g_all

p2g_mat=as.data.frame(peak2genelinkmat@listData[["ATAC"]]$matrix)
p2g_kmean=as.data.frame(peak2genelinkmat@listData[["ATAC"]]$kmeansId)
rownames(p2g_kmean)=rownames(p2g_mat)
which((rownames(p2g_kmean)==rownames(p2g_all))==TRUE)
unique(p2g_kmean$`peak2genelinkmat@listData[["ATAC"]]$kmeansId`)
plotPDF(p, name = "D7d20_Plot-Heatmap_peak2genelinks-scRNA_scATAC_blueyellow_purpleOrange_updated.pdf", ArchRProj = paracetP5, addDOC = TRUE, width = 6, height = 16)

######extraction of data of peak2genelinks ######

p2g_all$genepeak <- paste(p2g_all$gene,p2g_all$peak,sep=":")
mergedp2g$genepeak <- paste(mergedp2g$geneName,mergedp2g$peakName,sep=":")
alldat <- merge(mergedp2g,p2g_all,by="genepeak")
#writing data for all p2glinks  and kmeans for all data 
write.table(alldat,"_paracet_peak2genelinks_day7d20_alldatakmeans_corr_0.45.txt")


```
#D0-D20Peak2genelink
```{r peak2gene day 20} 
head(paracetP5$Sample)
idxSample <- BiocGenerics::which(paracetP5$Sample %in% "D20")
cellsSample <- paracetP5$cellNames[idxSample]
day20_archr <- paracetP5[cellsSample, ]
day20_archr <- addPeak2GeneLinks(
    ArchRProj = day20_archr,
    reducedDims = "IterativeLSI",
    useMatrix = "GeneIntegrationMatrix"
    )
p2g_d20 <- getPeak2GeneLinks(
    ArchRProj = day20_archr,
    corCutOff = 0.45,
    resolution = 1,
    returnLoops = FALSE
)
p2g_d20
metadata(p2g_d20)



p2g_d20$geneName <- mcols(metadata(p2g_d20)$geneSet)$name[p2g_d20$idxRNA]
tssgenes<- as.data.frame(metadata(p2g_d20)$geneSet)
colnames(tssgenes)[2] <- "StartTSS"
colnames(tssgenes)[3] <- "EndTSS"
p2g_d20$peakName <- (metadata(p2g_d20)$peakSet %>% {paste0(seqnames(.), "_", start(.), "_", end(.))})[p2g_d20$idxATAC]
p2g_d20_df=as.data.frame(p2g_d20)
temp  <- strsplit(p2g_d20$peakName, "_")
temp <- matrix(unlist(temp), ncol=3, byrow=TRUE)
temp <- as.data.frame(temp)
p2g_d20_df$chr <- temp$V1
p2g_d20_df$start <- temp$V2
p2g_d20_df$end <- temp$V3
mergedp2g_d20 <- merge(p2g_d20_df,tssgenes ,by.x="geneName", by.y= "name")
mergedp2g_d20$peakCentre=as.numeric(mergedp2g_d20$start)+250
mergedp2g_d20$looplength=as.numeric(mergedp2g_d20$StartTSS)-as.numeric(mergedp2g_d20$peakCentre)
#writes peak2genelink table
write.table(mergedp2g_d20,"day20ctrl_paracet_peak2genelinks_corr_0.45_res-1_loopobject.txt")

p_d20 <- plotPeak2GeneHeatmap(ArchRProj = day20_archr, groupBy = "Clusters2",
seed = 1,
  palATAC = paletteContinuous("coolwarm"),
  palRNA = paletteContinuous("blueYellow"),
  corCutOff = 0.45,
  FDRCutOff = 1e-04,
  k = 5,
palGroup = c('P3' = '#8175AA','P9' = '#8CC2CA','P5' = '#B15928',  'P10' = '#C0D6E4', 'P13' = '#A3ECB9')
)
#plotPDF(p_d20, name = "d20ctrl_Paracet_5_Plot-Heatmap_peak2genelinks-scRNA_scATAC_blueyellow_purpleOrange_updated.pdf",pal = constrained_palette, ArchRProj = day20_archr, addDOC = TRUE, width = 6, height = 16)



#plotPDF(p_d20, name = "d20ctrl_Paracet_5_Plot-Heatmap_peak2genelinks-scRNA_scATAC_blueyellow_purpleOrange_updated.pdf",pal = constrained_palette, ArchRProj = day20_archr, addDOC = TRUE, width = 6, height = 16)
p_d20
dev.copy(pdf,paste0("__d20ctrl_Paracet_5_Plot-Heatmap_peak2genelinks-scRNA_scATAC_blueyellow_purpleOrange_updated.pdf"), width=6, height=16, paper='special')
dev.off() 

#to obtain matrices for kmeans returnMatrices= TRUE
peak2genelink_d20 <- plotPeak2GeneHeatmap(ArchRProj = day20_archr, 
  groupBy = "Clusters2",
  seed = 1,
  palATAC = paletteContinuous("coolwarm"),
  palRNA = paletteContinuous("blueYellow"),
  corCutOff = 0.45,
  FDRCutOff = 1e-04,
returnMatrices = TRUE,
 k = 5,
nPlot = 100000 
)
#fetching kmeans for ATAC and RNA 
p2gl_d20 <- as.data.frame(peak2genelink_d20@listData[["Peak2GeneLinks"]])
p2g_d20_atac <- as.data.frame(peak2genelink_d20@listData[["ATAC"]]@listData[["kmeansId"]])
p2gl_d20$kmeansATAC <- p2g_d20_atac$`peak2genelink_d20@listData[["ATAC"]]@listData[["kmeansId"]]`
p2g_d20_rna <- as.data.frame(peak2genelink_d20@listData[["RNA"]]@listData[["kmeansId"]])
p2gl_d20$kmeansRNA <- p2g_d20_rna$`peak2genelink_d20@listData[["RNA"]]@listData[["kmeansId"]]`
p2gl_d20$peak <- str_replace(p2gl_d20$peak,":","_")
p2gl_d20$peak <- str_replace(p2gl_d20$peak,"-","_")
p2gl_d20

##checking if the kmeans are merged correctly
p2gl_d20_mat=as.data.frame(peak2genelink_d20@listData[["ATAC"]]$matrix)
p2gl_d20_kmean=as.data.frame(peak2genelink_d20@listData[["ATAC"]]$kmeansId)
rownames(p2gl_d20_kmean)=rownames(p2gl_d20_mat)
which((rownames(p2gl_d20_kmean)==rownames(p2gl_d20))==TRUE)
unique(p2gl_d20_kmean$`peak2genelink_d20@listData[["ATAC"]]$kmeansId`)

######extraction of data of peak2genelinks ######

p2gl_d20$genepeak <- paste(p2gl_d20$gene,p2gl_d20$peak,sep=":")

mergedp2g_d20$genepeak <- paste(mergedp2g_d20$geneName,mergedp2g_d20$peakName,sep=":")
alldat_d20<- merge(mergedp2g_d20,p2gl_d20,by="genepeak")

library(rGREAT)
bed =  subset(alldat_d20, select = c(chr,start,end,kmeansATAC))
bed$start <- as.numeric(bed$start)
bed$end <- as.numeric(bed$end)
bed
kmeans1 <- bed[bed$kmeansATAC == '1', ]
bedKmeans =  subset(kmeans1, select = c(chr,start,end))
job = submitGreatJob(bedKmeans,species = "hg38")
tb = getEnrichmentTables(job)
res = plotRegionGeneAssociationGraphs(job)
dev.copy(pdf,paste0(currentjob,"day20ctrl_top25000rgreatanalysis_d20ctrl_kmeans1"), height=5, width=8)
dev.off()
#tb = getEnrichmentTables((job), download_by = 'tsv')
write.table(tb$`GO Biological Process`,"_d20ctrl_top25000_kmeans1_bioloigical_process.tsv")



kmeans2 <- bed[bed$kmeansATAC == '2', ]
bedKmeans =  subset(kmeans2, select = c(chr,start,end))
job = submitGreatJob(bedKmeans,species = "hg38")
tb = getEnrichmentTables(job)
res = plotRegionGeneAssociationGraphs(job)
dev.copy(pdf,paste0(currentjob,"_day20ctrl_rgreatanalysisd20kmeans2"), height=5, width=8)
dev.off()
#tb = getEnrichmentTables((job), download_by = 'tsv')
write.table(tb$`GO Biological Process`,"_day20ctrl_kmeans2_bioloigical_process.tsv")


kmeans3 <- bed[bed$kmeansATAC == '3', ]
bedKmeans =  subset(kmeans3, select = c(chr,start,end))
job = submitGreatJob(bedKmeans,species = "hg38")
tb = getEnrichmentTables(job)
res = plotRegionGeneAssociationGraphs(job)
dev.copy(pdf,paste0(currentjob,"_day20ctrl_rgreatanalysisd20kmeans3"), height=5, width=8)
dev.off()
#tb = getEnrichmentTables((job), download_by = 'tsv')
write.table(tb$`GO Biological Process`,"_day20ctrl_kmeans3_bioloigical_process.tsv")



kmeans4 <- bed[bed$kmeansATAC == '4', ]
bedKmeans =  subset(kmeans4, select = c(chr,start,end))
job = submitGreatJob(bedKmeans,species = "hg38")
tb = getEnrichmentTables(job)
res = plotRegionGeneAssociationGraphs(job)
dev.copy(pdf,paste0(currentjob,"_day20ctrl_rgreatanalysisd20kmeans4"), height=5, width=8)
dev.off()
#tb = getEnrichmentTables((job), download_by = 'tsv')
write.table(tb$`GO Biological Process`,"_day20ctrl_kmeans4_bioloigical_process.tsv")

kmeans5 <- bed[bed$kmeansATAC == '5', ]
bedKmeans =  subset(kmeans5, select = c(chr,start,end))
job = submitGreatJob(bedKmeans,species = "hg38")
tb = getEnrichmentTables(job)
res = plotRegionGeneAssociationGraphs(job)
dev.copy(pdf,paste0(currentjob,"_day20ctrl_rgreatanalysisd20kmeans5"), height=5, width=8)
dev.off()
#tb = getEnrichmentTables((job), download_by = 'tsv')
write.table(tb$`GO Biological Process`,"_day20ctrl_kmeans5_bioloigical_process.tsv")


library(dplyr)
kmeans1_GO <- alldat_d20[alldat_d20$kmeansATAC == '1', ]
kmeans1_GO <-  filter(kmeans1_GO, Correlation.x  > 0.7 & FDR.x<1e-4)
kmeans2_GO <- alldat_d20[alldat_d20$kmeansATAC == '2', ]
kmeans2_GO <- filter(kmeans2_GO, Correlation.x  > 0.7 & FDR.x<1e-4)
kmeans3_GO <- alldat_d20[alldat_d20$kmeansATAC == '3', ]
kmeans3_GO <- filter(kmeans3_GO, Correlation.x  > 0.7 & FDR.x<1e-4)
kmeans4_GO <- alldat_d20[alldat_d20$kmeansATAC == '4', ]
kmeans4_GO <- filter(kmeans4_GO, Correlation.x  > 0.7 & FDR.x<1e-4)
kmeans5_GO <- alldat_d20[alldat_d20$kmeansATAC == '5', ]
kmeans5_GO <- filter(kmeans5_GO, Correlation.x  > 0.7 & FDR.x<1e-4)
mylist <- list()
mylist[[1]] <- kmeans1_GO$gene
mylist[[2]] <- kmeans2_GO$gene
mylist[[3]] <- kmeans3_GO$gene
mylist[[4]] <- kmeans4_GO$gene
mylist[[5]] <- kmeans5_GO$gene
```
#gprofilerAnnotations
```{r genelist annotation}
library(gprofiler2)
######################################################################################################
##for using custom annotation 
# upload_GMT_file(gmtfile = "/MSIGDB/c7.immunesigdb.v7.4.symbols.gmt")
# upload_GMT_file(gmtfile = "/MSIGDB/h.all.v7.4.symbols.gmt")

###
#GOprofiler analysis 
######################################################################################################
multi_gostres1 <- gost(query =mylist, sources = c("GO:BP"),
                       multi_query = TRUE)
publish_gosttable(multi_gostres1, 
                  highlight_terms = multi_gostres1$result[c(1:20),],
                  use_colors = TRUE, 
                  show_columns = c("source", "term_name", "term_size"),
                  filename = NULL)+
  ggtitle('Biological Processes')
dev.copy(pdf,paste0("_D20ctrl_gprofiler_Kmeans_corr_0.7_significant_",currentjob,".pdf"), width=16, height=12,paper='special')
dev.off()
gostplot(multi_gostres1, capped = TRUE, interactive = TRUE)
fwrite(multi_gostres1$result, file ="_d20ctrl_gprofiler_kmeans_gostplot_corrgreaterthan0.7_significant.csv")

```

#gprofilerAnnotationsd0
```{r Plots counts pergene}
library(gprofiler2)
library(data.table)

######################################################################################################
##for using custom annotation 
# upload_GMT_file(gmtfile = "/MSIGDB/c7.immunesigdb.v7.4.symbols.gmt")
# upload_GMT_file(gmtfile = "/MSIGDB/h.all.v7.4.symbols.gmt")

#GOprofiler analysis 
######################################################################################################
library(dplyr)
kmeans1_GO <- alldat_d20[alldat_d20$kmeansATAC == '1', ]
kmeans1_GO <-  filter(kmeans1_GO, Correlation.x  > 0.45 & FDR.x<1e-4)
kmeans2_GO <- alldat_d20[alldat_d20$kmeansATAC == '2', ]
kmeans2_GO <- filter(kmeans2_GO, Correlation.x  > 0.45 & FDR.x<1e-4)
kmeans3_GO <- alldat_d20[alldat_d20$kmeansATAC == '3', ]
kmeans3_GO <- filter(kmeans3_GO, Correlation.x  > 0.45 & FDR.x<1e-4)
kmeans4_GO <- alldat_d20[alldat_d20$kmeansATAC == '4', ]
kmeans4_GO <- filter(kmeans4_GO, Correlation.x  > 0.45 & FDR.x<1e-4)
kmeans5_GO <- alldat_d20[alldat_d20$kmeansATAC == '5', ]
kmeans5_GO <- filter(kmeans5_GO, Correlation.x  > 0.45 & FDR.x<1e-4)
mylist <- list()
mylist[[1]] <- kmeans1_GO$gene
mylist[[2]] <- kmeans2_GO$gene
mylist[[3]] <- kmeans3_GO$gene
mylist[[4]] <- kmeans4_GO$gene
mylist[[5]] <- kmeans5_GO$gene

multi_gostres1 <- gost(query =mylist, sources = c("GO:BP"),
                       multi_query = TRUE)
publish_gosttable(multi_gostres1, 
                  highlight_terms = multi_gostres1$result[c(1:20),],
                  use_colors = TRUE, 
                  show_columns = c("source", "term_name", "term_size"),
                  filename = NULL)+
  ggtitle('Biological Processes')
dev.copy(pdf,paste0("_D20ctrl_gprofiler__Kmeans_corr_0.45_significant_",currentjob,".pdf"), width=16, height=12,paper='special')
dev.off()
gostplot(multi_gostres1, capped = TRUE, interactive = FALSE)
dev.copy(pdf,paste0("_D20_Ctrl_gprofiler_gostplot__Kmeans_corr_0.45_significant_",currentjob,".pdf"), width=16, height=8,paper='special')
fwrite(multi_gostres1$result, file ="_D20_ctrl_gprofiler_kmeans_gostplot_corrgreaterthan0.45_significant.csv")


```



#day20PositivetfRegulator

```{r motif footprinting day20 } 
seGroupMotif <- getGroupSE(ArchRProj = day20_archr , useMatrix = "MotifMatrix", groupBy = "Clusters2")
seZ <- seGroupMotif[rowData(seGroupMotif)$seqnames=="z",]


rowData(seZ)$maxDelta <- lapply(seq_len(ncol(seZ)), function(x){
  rowMaxs(assay(seZ) - assay(seZ)[,x])
}) %>% Reduce("cbind", .) %>% rowMaxs



corGSM_MM_d20 <- correlateMatrices(
    ArchRProj = day20_archr,
    useMatrix1 = "GeneScoreMatrix",
    useMatrix2 = "MotifMatrix",
    reducedDims = "IterativeLSI"
)


corGIM_MM_d20 <- correlateMatrices(
    ArchRProj = day20_archr,
    useMatrix1 = "GeneIntegrationMatrix",
    useMatrix2 = "MotifMatrix",
    reducedDims = "IterativeLSI"
)
corGIM_MM_d20

corGSM_MM_d20$maxDelta <- rowData(seZ)[match(corGSM_MM_d20$MotifMatrix_name, rowData(seZ)$name), "maxDelta"]
corGIM_MM_d20$maxDelta <- rowData(seZ)[match(corGIM_MM_d20$MotifMatrix_name, rowData(seZ)$name), "maxDelta"]
corGSM_MM_d20 <- corGSM_MM_d20[order(abs(corGSM_MM_d20$cor), decreasing = TRUE), ]
corGSM_MM_d20 <- corGSM_MM_d20[which(!duplicated(gsub("\\-.*","",corGSM_MM_d20[,"MotifMatrix_name"]))), ]
corGSM_MM_d20$TFRegulator <- "NO"
corGSM_MM_d20$TFRegulator[which(corGSM_MM_d20$cor > 0.4 & corGSM_MM_d20$pval < 0.01 & corGSM_MM_d20$maxDelta > quantile(corGSM_MM_d20$maxDelta, 0.5))] <- "YES"
sort(corGSM_MM_d20[corGSM_MM_d20$TFRegulator=="YES",1])
name_matrix=c('NHLH1','NHLH2','ISL1','REL','NEUROD1','NEUROG1','SP1','OTX2','YY2','KLF4')
library(ggrepel)
p_GSM_d20 <- ggplot(data.frame(corGSM_MM_d20), aes(cor, maxDelta, color = TFRegulator)) +
  geom_text_repel(
    data = subset(data.frame(corGSM_MM_d20), corGSM_MM_d20$cor > 0.4 & corGSM_MM_d20$pval < 0.01),

    aes(label = MotifMatrix_name),
    size = 1.5,
    box.padding = unit(0.2, "lines"),
    point.padding = unit(0.2, "lines"))+
  geom_point() + 
  theme_ArchR() +
  geom_vline(xintercept = 0, lty = "dashed") + 
 
  scale_color_manual(values = c("NO"="darkgrey", "YES"="firebrick3")) +
  xlab("Correlation To Gene Score") +
  ylab("Max TF Motif Delta") +
  scale_y_continuous(
    expand = c(0,0), 
    limits = c(0, max(corGSM_MM_d20$maxDelta)*1.05)
  )
library(ggplot2)
p_GSM_d20
dev.copy(pdf,paste0("_D20_ctrl_positiveTFRegulators_genescorematrixpvalue_smaller label",currentjob,".pdf"), width=8, height=10,paper='special')
dev.off()

corGIM_MM_d20<- corGIM_MM_d20[order(abs(corGIM_MM_d20$cor), decreasing = TRUE), ]
corGIM_MM_d20 <- corGIM_MM_d20[which(!duplicated(gsub("\\-.*","",corGIM_MM_d20[,"MotifMatrix_name"]))), ]
corGIM_MM_d20$TFRegulator <- "NO"
corGIM_MM_d20$TFRegulator[which(corGIM_MM_d20$cor > 0.4 & corGIM_MM_d20$pval < 0.01 & corGIM_MM_d20$maxDelta > quantile(corGIM_MM_d20$maxDelta, 0.5))] <- "YES"
sort(corGIM_MM_d20[corGIM_MM_d20$TFRegulator=="YES",1])


p1_GIM_d20 <- ggplot(data.frame(corGIM_MM_d20), aes(cor, maxDelta, color = TFRegulator))+
  geom_text_repel(
    data = subset(data.frame(corGIM_MM_d20), corGIM_MM_d20$cor > 0.4 & corGIM_MM_d20$pval < 0.01),
    aes(label = MotifMatrix_name),
      
    size = 2,
    max.overlaps = 30,
    box.padding = unit(0.3, "lines"),
    point.padding = unit(0.3, "lines")
    )+
    geom_point() + 
    theme_ArchR() +
    geom_vline(xintercept = 0, lty = "dashed") + 
 
    scale_color_manual(values = c("NO"="darkgrey", "YES"="firebrick3")) +
    xlab("Correlation To Gene Score") +
    ylab("Max TF Motif Delta") +
    scale_y_continuous(
    expand = c(0,0), 
    limits = c(0, max(corGIM_MM_d20$maxDelta)*1.05)
  )


p1_GIM_d20
dev.copy(pdf,paste0("_D20ctrl_positiveTFRegulators_geneintegrationmatrix_smaller_label",currentjob,".pdf"), width=8, height=10,paper='special')
dev.off()

write.table(corGIM_MM_d20,"D20.ctrl_geneintegrationmatrix_positivetfRegulator_all.tsv")

```



####################
###################


#Umaps D0/D20 separately
```{r Umaps } 
ArchRPalettes$custom <-c('R0' = '#CCCCCC','R2'= '#DAB6AF', 'R3'='#023858','R7' = '#8175AA','R9' = '#FFC966','R12' ='#8CC2CA')
constrained_palette <- ArchRPalettes$custom

p2_d20_umap <- plotEmbedding(
     day20_archr, 
    reducedDims = "IterativeLSI",
    colorBy = "cellColData", 
    name = "predictedGroup_Co", 
    pal = constrained_palette,
    rastr = FALSE,
    size=0.3
)
p2_d20_umap



plotPDF(p2_d20_umap, name = "d20_Plot-UMAP-constrained-d20_final-names-Clusters.pdf", ArchRProj = day20_archr, addDOC = TRUE, width = 5, height = 5)

p2_d0_umap <- plotEmbedding(
     day0_archr, 
    reducedDims = "IterativeLSI",
    colorBy = "cellColData", 
    name = "predictedGroup_Co", 
    pal = constrained_palette,
    rastr = FALSE,
    size=0.3
)
p2_d0_umap

plotPDF(p2_d0_umap, name = "d0_Plot-UMAP-constrained-d20_final-names-Clusters.pdf", ArchRProj = day20_archr, addDOC = TRUE, width = 5, height = 5)
```

##End of the script


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
